Forecasting the 2024 Election: Trump Dominates the South, Harris Leads in the Midwest

### 2024-10-22 paper/paper.qmd
committing text changes to paper.qmd

### Model Diagnostics Result
[@fig-barplot-diagnostics] displays the performance of the Bayesian logistic regression model used to predict the outcome of the 2024 presidential election. The model's accuracy is approximately 75%, indicating that 75% of the test set's state-level outcomes were correctly predicted. The RMSE (Root Mean Squared Error) is about 0.5, showing the average error in predicting the winning candidate across states. This suggests the model performs reasonably well, but there is some error in predicting the exact outcome in certain states, which may be due to variations in polling data or other unaccounted factors.

@@

# Visualizing the RMSE and accuracy in a plot with skinnier bars
ggplot(accuracy_rmse_df, aes(x = Metric, y = Value)) +
  geom_bar(stat = "identity", fill = "steelblue", width = 0.2) +  # Adjusted width for skinnier bars
  labs(y = "Value") +
  theme_light()
```
\newpage

>>>>

### Model Diagnostics Result

@@

# Visualizing the RMSE and accuracy in a plot with skinnier bars
ggplot(accuracy_rmse_df, aes(x = Metric, y = Value)) +
  geom_bar(stat = "identity", fill = "steelblue", width = 0.2) +  # Adjusted width for skinnier bars
  labs(y = "Value") +
  theme_light()
```
[@fig-barplot-diagnostics] displays the performance of the Bayesian logistic regression model used to predict the outcome of the 2024 presidential election. The model's accuracy is approximately 75%, indicating that 75% of the test set's state-level outcomes were correctly predicted. The RMSE (Root Mean Squared Error) is about 0.5, showing the average error in predicting the winning candidate across states. This suggests the model performs reasonably well, but there is some error in predicting the exact outcome in certain states, which may be due to variations in polling data or other unaccounted factors.
